Fair, Stable Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs

### 2019-06-25 writing/Paper/main.tex

\begin{figure}[[p!htb] % p stands for 'entire page', '!htb' is to insert as close to code as possible
  \floatpagestyle{empty} % remove page number
  \centering
  \vspace{-2cm} % shift upwards to get more space for caption
  \includegraphics[width=\linewidth]{static_game.png}
  \caption{\small{
  		The balancing effect of the distance-based tax is demonstrated. 
		The first two rows depict an economy where the is no distance-based tax. 
		If costs are equal, the profits are equal as well. 
		But if costs are marginally different, the game-theoretical equilibrium profit are disproportionally large. 
		The mitigating effect of a distance-based tax is considered in rows 3-5. 
		If costs are equal (row 3) or marginally different (row 4), then profits are only marginally different. 
		But if costs are significantly different (row 5), so are the equilibrium profits. 
		An interpretation in an economic context is provided in the text of subsection \ref{sec:static_game}. 
		 }}
  \label{fig:static_game}
\end{figure}

@@

In the previous subsection, we have demonstrated how a distance-tax-free $\gamma=0$ economy disproportionally rewards essentially random, minor differences in firm competitiveness. 
But even more concerningly, the problem does not stay static: 
This disproportional revenue can be used to further invest in aggressive marketing, thereby increasing the difference between the two firms even more. 
This may ultimately run a firm out of business, although it was initially effectively competitive as the other firms.

>>>>

\begin{figure}[[p!htb] % p stands for 'entire page', '!htb' is to insert as close to code as possible
  \floatpagestyle{empty} % remove page number
  \centering
  \vspace{-2cm} % shift upwards to get more space for caption
  \includegraphics[width=\linewidth]{static_game.png}
  \caption{\small{
  		The balancing effect of the distance-based tax is demonstrated. 
		The first two rows depict an economy where the is no distance-based tax. 
		If costs are equal, the profits are equal as well. 
		But if costs are marginally different, the game-theoretical equilibrium profit are disproportionally large. 
		The mitigating effect of a distance-based tax is considered in rows 3-5. 
		If costs are equal (row 3) or marginally different (row 4), then profits are only marginally different. 
		But if costs are significantly different (row 5), so are the equilibrium profits. 
		An interpretation in an economic context is provided in the text of subsection \ref{sec:static_economy}. 
		 }}
  \label{fig:static_game}
\end{figure}

@@

In the previous subsection, we have demonstrated how a distance-tax-free economy disproportionally rewards essentially random, minor differences in firm competitiveness. 
But even more concerningly, the problem does not stay static: 
This disproportional revenue can be used to further invest in aggressive marketing, thereby increasing the difference between the two firms even more. 
This may ultimately run a firm out of business, although it was initially as competitive as the other firms.
